Can money buy happiness?

### 2022-04-29 draft2.Rmd
Fixed caption

ggplotly(GDPP_hours,
         width = 800,
         height = 430,
         tooltip = c("text", 
                     "x",
                     "y",
                     "City")) 
```

>>>>

ggplotly(GDPP_hours,
         width = 800,
         height = 430,
         tooltip = c("text", 
                     "x",
                     "y",
                     "City")) %>% 
layout(title = list(text = paste0('Gross Domestic Product per Capita by Country and Average Weekly Hours Worked',
                                    '<br>',
                                    '<sup>',
                                    'Data sourced from Kaggle and World Population Review',
                                    '</sup>')))
```
